### 2019-09-13 README.Rmd
Changed geneList bubble colors in flow chart

## Build flow chart
for (i in 1:nr){
  arrpos[i, ] <- straightarrow (to = elpos[fromto[i, 2], ],
                                from = elpos[fromto[i, 1], ],
                                lwd = 2, arr.pos = 0.6, arr.length = 0.5)
  textellipse(elpos[1,], 0.10, 0.04, lab = "geneList1", box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[2,], 0.10, 0.03, lab = "get_kegg()", box.col = "steelblue1",
              shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[3,], 0.10, 0.04, lab = "geneList2", box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textround(elpos[4,], 0.10, 0.03,lab = "KEGG REST API", box.col = "orange1",
            shadow.col = "orange4", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[5,], 0.15, 0.04, lab = c("cleaned gene-to-pathway", "map"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[6,], 0.10, 0.03,lab = "pathEnrich(List 1)", box.col = "steelblue1",
            shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[7,], 0.10, 0.03, lab = "pathEnrich(List 2)", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[8,], 0.10, 0.04, lab = c("pathEnrich","result/object"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[9,], 0.10, 0.04, lab = c("pathEnrich","result/object"),box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[10,], 0.10, 0.03, lab = "diffEnrich()", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[11,], 0.10, 0.04, lab = c("diffEnrich","result/object"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[12,], 0.11, 0.03, lab = "plotFoldEnrichment", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  text(0.15,0.05, "Figure 1. diffEnrich Analysis pipeline", cex = 0.75)
}
```

>>>>

## Build flow chart
for (i in 1:nr){
  arrpos[i, ] <- straightarrow (to = elpos[fromto[i, 2], ],
                                from = elpos[fromto[i, 1], ],
                                lwd = 2, arr.pos = 0.6, arr.length = 0.5)
  textellipse(elpos[1,], 0.10, 0.04, lab = "geneList1", box.col = "purple",
              shadow.col = "purple4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[2,], 0.10, 0.03, lab = "get_kegg()", box.col = "steelblue1",
              shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[3,], 0.10, 0.04, lab = "geneList2", box.col = "purple",
              shadow.col = "purple4", shadow.size = 0.005, cex = 1.0)
  textround(elpos[4,], 0.10, 0.03,lab = "KEGG REST API", box.col = "orange1",
            shadow.col = "orange4", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[5,], 0.15, 0.04, lab = c("cleaned gene-to-pathway", "map"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[6,], 0.10, 0.03,lab = "pathEnrich(List 1)", box.col = "steelblue1",
            shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[7,], 0.10, 0.03, lab = "pathEnrich(List 2)", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[8,], 0.10, 0.04, lab = c("pathEnrich","result/object"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[9,], 0.10, 0.04, lab = c("pathEnrich","result/object"),box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[10,], 0.10, 0.03, lab = "diffEnrich()", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[11,], 0.10, 0.04, lab = c("diffEnrich","result/object"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[12,], 0.11, 0.03, lab = "plotFoldEnrichment", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  text(0.15,0.05, "Figure 1. diffEnrich Analysis pipeline", cex = 0.75)
}
```
